---
title: "Assignment 4"
author: "Huong Tran"
date: "11/24/2021"
output: pdf_document
---
```{r}
data <- read.table("cap3.txt", header = T)
attach(data)
n <- nrow(data)
library(survey)
```
1. Compute an estimate of population mean for variable "growth" along with the standard error.

```{r}
fpc <- 1:n
fpc[stype == 'E'] <- 4421
fpc[stype == 'M'] <- 1018
fpc[stype == 'H'] <- 755 

sv <- svydesign(id=~ dnum, strata = stype, data = data, fpc =~ fpc, nest = TRUE)
svymean(~growth, sv)
```

b. Regression analysis to assess if there is a linear relationship between the "growth" and "awards, "meal" and "colgrad".
```{r}
summary(svyglm(growth ~ awards + meals + colgrad, design = sv))
```
Based on P-value, we conclude that eligibility for awards and the percentage of students eligible for subsidized meals can help predict the change in academic performacne index from 1999 to 2000.
c. 

```{r}
summary(svyglm(I(grsign == 1) ~awards + meals + colgrad , design = sv, family=binomial(link = "logit"))) 
```
Using p-value, we conclude that there is relationship between the eligibility for award and "grsign".

d. 
```{r}
svytable(~grsign + awards, sv)

```
```{r}
svychisq(~grsign + awards, sv,statistic = "Wald")
```

Using Wald test, we obtain small p-value, which indicate the relationship between "grsign" and "awards", and this result agrees with the conclusion in part c. 