---
title: "The effect of milk on LDL Cholesterol level"
author: "Huong Tran"
date: "11/26/2021"
fontsize: 10pt
output:
  beamer_presentation:
    theme: "Warsaw"
    colortheme: "default"
    fonttheme: "structurebold"
    
---

## Objective:
-  Low-density lipoprotein (LLD) cholesterol level is the main reason causing heart disease and heart attack.
-  Consuming whole-fat dairy product can have unwanted health effect of increasing  LDL cholesterol level
- This project identifies the affect of several types of milk on LDL cholesterol level.


## Data Resource: 

- From National Health and Nutrition Examination Survey (NHANES), year 2017 - 2018.
- Population: 320,842,721
- Sample size: 16,211
- The screener response rate: 90.9%
- 9,254 completed the interview and 8,704 were examined.



## About Survey Design:
The following components are used:

- Questionnaire Data: we extract information about the choice of milk.
- Laboratory Data:  the measure of LDL cholesterol (mg/dL) using  the standard Fredewald equation. 

Note: triglyceride less than 400mg/dL.

- Demographic: sample weight, PSUs, stratum information. 
- Using "SEQN" to merge data.

## About Survey Design: 
- Selection of PSUs, which are counties: these PSUs were selected from strata defined by geography, metropolitan statistical area status, and various population demographics. Two PSUs were selected from most strata.

    Note that if counties has the population of less than 5000, it will be combined with the adjacent counties to have the required number of population.
-  Selection of segments within PSUs, that constitute a block/or group of blocks containing a cluster of households.
-  Selection of specific households with segments, generally are city blocks.
-  Selection of individual within household.

## About Survey Design:

\begin{center}
  \includegraphics{/Users/huongtran/OU /Course Work/SES 3/STA5229/Final Project/result/pic_design.png}
\end{center}

## Demographics component:
- Demographics: 
    + SDMVSTRA: masked variance unit pseudo-stratum.
    + SDMVPSU: massked variance unit psedo-PSU.
    + WTMEC2YR: sampling weight.

## Questionnaire component:

- Questionnaire components:
    + DBQ223A: You drink whole or regular milk.
    + DBQ223B: You drink 2\% fat milk.
    + DBQ223C: You drink 1\% fat milk. 
    + DBQ223D: You drink fat free/skim milk.
    + DBQ223E: You drink soy milk.
    + DBQ223U: You drink another type of milk. 
     
     
     
## Laboratory component:
- Laboratory Data: LBDLDL:  measure of LDL cholesterol (mg/dL) using  the standard Fredewald equation. 

## Restriction: 
- We are ignoring the requirement for triglyceride less than 400mg/dL in this project.

- The cholesterol measure is valid for 12-year-older participants while the questionnaire for Diet and Behaviour are subjected for all participant. 


```{r echo = F, message = F, warning = F}

library(foreign)
library(survey)
library(dplyr)
library(tidyr)
library(survey)
library(gridExtra)
library(ggplot2)
library(Hmisc)
```


```{r, echo=FALSE}
milk <- read.xport("/Users/huongtran/OU /Course Work/SES 3/STA5229/Final Project/dataset/DBQ_J.xpt")
choles <- read.xport("/Users/huongtran/OU /Course Work/SES 3/STA5229/Final Project/dataset/TRIGLY_J.xpt")
demo <- read.xport("/Users/huongtran/OU /Course Work/SES 3/STA5229/Final Project/dataset/DEMO_J.xpt")

# save as an R data frame
saveRDS(milk, file="/Users/huongtran/OU /Course Work/SES 3/STA5229/Final Project/dataset/DEMO_I.rds")
saveRDS(choles, file="/Users/huongtran/OU /Course Work/SES 3/STA5229/Final Project/dataset/TRIGLY_J.rds")
saveRDS(demo, file="/Users/huongtran/OU /Course Work/SES 3/STA5229/Final Project/dataset/DEMO_J.rds")
```


```{r, echo= F}
df <- left_join(select(demo, "SEQN", starts_with("SDMV"), "WTMEC2YR"), 
                select(milk, "SEQN", starts_with("DBQ223")), by="SEQN") %>%
  left_join(., select(choles, "SEQN", "LBDLDL") , by="SEQN")
```
 

 

## Data Exploratory: 

\begin{center}
  \includegraphics{/Users/huongtran/OU /Course Work/SES 3/STA5229/Final Project/result/df.png}
\end{center}



## Data Exploratory:
- Some observations give answer in at least 2 types of milk:
```{r}
select(df, "DBQ223A", "DBQ223B", "DBQ223C", "LBDLDL")[21:23,]
```


## Data Exploratory:
- Gather observations giving answer on at least 2 types of milk.
- Create new varialbe called "Category": 

```{r, echo = F}
for (i in 1:nrow(df) ){
  if (is.na(df$DBQ223A[i]) == T & is.na(df$DBQ223B[i]) == T & is.na(df$DBQ223C[i]) == T &
      is.na(df$DBQ223D[i]) == T & is.na(df$DBQ223E[i]) == T & is.na(df$DBQ223U[i]) == T)  {
    df$Category[i] = NA}
  else {
    t <- sum(df$DBQ223A[i], df$DBQ223B[i], df$DBQ223C[i], df$DBQ223D[i], df$DBQ223E[i], df$DBQ223U[i], na.rm = T)
    if (t== 10) {
      df$Category[i] <- "whole milk"
    } else if ( t == 99) {
      df$Category[i] <- "don't know"
    } else if (t == 11) {
      df$Category[i] <- "2% fat"
    } else if (t == 12) {
      df$Category[i] <- "1% fat" 
    } else if (t == 13) {
      df$Category[i] <- "fat free"
    } else if (t == 14) {
      df$Category[i] <- "soy milk"
    } else if (t == 30) {
      df$Category[i] <- "another"
    } else {
      df$Category[i] <- "2 types"
    }
  }
}
```


```{r}
as.matrix(unique(df$Category))
```


## Data Exploratory: 
- Delete the others columns:
```{r, size = "huge"}
df <- select(df, - starts_with("DBQ223"))
head(df)
```

## Survey Design:
```{r}
sv <- svydesign(id=~SDMVPSU,  strata =~SDMVSTRA, 
                data=df, weights=~WTMEC2YR,nest=TRUE)

deff(df$LBDLDL, cluster = df$SDMVPSU)
```

Which implies that our design is less precise than SRS.

## About LDL Cholesterol:
```{r}
plot(svycdf(~LBDLDL, sv),
     main= "Population of LDL Cholesterol level", col = "blue")
```

## About LDL Cholesterol:
```{r, }
svyplot(~LBDLDL, sv, basecol = "blue",
        main = "Scatterplot for sampling weights")
```

## Survey Design:
 - Consider the survey on sub-population for observations having their answer on a specific type of milk:
```{r}
sub.sv <- subset(sv, is.na(df$Category) == F & 
                   df$Category != "2 types" & 
                   df$Category != "don't know")
```




## Estimate of mean:
```{r}
svyboxplot(LBDLDL ~ Category, design = sub.sv,
            main = "Boxplot of LDL Cholesterol level/each types of milk")

```

## Estimate of mean and confidence interval: 
```{r}
mean <- svyby(~LBDLDL,~Category, design =  sub.sv, 
              svymean, na.rm = T)
select(cbind(mean, confint(mean)), -"Category")
```


## Using Regression:
```{r}
model <- svyglm(LBDLDL ~ Category, design = sub.sv )
s <- summary(model)$coefficients
print(s, digits = 2)
```

## Whole milk and non-fat milk:
Test the following hypothesis:
$$H_0: \bar{y}_{10} = \bar{y}_{13}$$ 

```{r}
sub.sv2 <- subset(sv, df$Category == "whole milk" | 
                    df$Category == "fat free")
svyttest(LBDLDL~Category, sub.sv2) 
```


## Whole milk and non-fat milk:
$$p-\text{value} = 0.7644 > 0.05$$ 
Since the computed $p-value$ does not fall in the rejection region, we fail to reject $H_0$. There is insufficient evidence (at $\alpha = 0.05$)  of a difference between the true mean LDL Cholesterol between people who drink whole milk and people who drink fat free milk.

## Further question:
1.  The requirement of Fredewald equation?
2.  Considering the effect of observations who drink at least 2 types of milk at the same time.

## Reference:
1. Sampling: Design and Analysis, Second Edition - Sharon Lohr.
2. https://cran.r-project.org/web/packages/survey/survey.pdf
3. https://wwwn.cdc.gov/nchs/nhanes/tutorials/default.aspx

## 
\begin{center}


  \Huge {Thank you!}


\end{center}
